Here is the updated LaTeX resume, focused on matching the job description:

\name{Eshanth Chinthareddy}
\address{Ames, Iowa · 612-461-6318 · chinthareddyeshanth@gmail.com}
\basicInfo{
  \email{chinthareddyeshanth@gmail.com} \textperiodcentered\ 
  \phone{612-461-6318} \textperiodcentered\ 
  \linkedin{eshanth-chinthareddy}
  \github{eshan-chinthareddy}
}

\section{Education}
\datedsubsection{\textbf{Iowa State University}, Ames, IA}{Dec 2025}
\textit{Bachelor of Science in Software Engineering}  \textperiodcentered\  GPA: 3.28

\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}{C/C++, Python, Java, C\#, .NET, Assembly, JavaScript, TypeScript, Go, HTML/CSS}
\resumeSubItem{Technologies}{Embedded Systems, Linux, NVIDIA Jetson, CStreamer, Git, REST APIs, AWS, GCP, Azure}
\resumeSubItem{Frameworks}{Spring Boot, Django, React, Redux, Electron, ASP.NET Core, Pandas, Selenium}
\resumeSubHeadingListEnd

\section{Experience}
\datedsubsection{\textbf{Thinix}, Ames, IA}{May 2024 – Present}
\role{Software Engineering Intern}{}
\resumeItemListStart
\resumeItem{Developed reporting tools with ASP.NET Core and Entity Framework to analyze system performance.}
\resumeItem{Optimized APIs using eager/lazy loading and async, reducing response times by 40\%.}
\resumeItem{Led .NET 6 to .NET 8 migration, enhancing scalability and efficiency.}
\resumeItem{Implemented automated testing pipelines with MSTest and Jest, increasing coverage.}
\resumeItemListEnd

\datedsubsection{\textbf{Iowa State University}, Ames, IA}{May 2023 – May 2024}
\role{System Support Specialist}{}
\resumeItemListStart
\resumeItem{Provided technical support, troubleshooting software/hardware issues and managing IT tickets.}
\resumeItem{Utilized SCCM and JAMF for software deployment, device configuration, and inventory tracking.}
\resumeItemListEnd

\datedsubsection{\textbf{Iowa State University}, Ames, IA}{Jan 2023 – May 2023}
\role{Mathematics Grading Assistant}{}  
\resumeItemListStart
\resumeItem{Assessed quizzes and assignments, providing feedback to improve problem-solving skills.}
\resumeItem{Mentored students in calculus and algebra through personalized tutoring sessions.}
\resumeItem{Implemented teaching methods to create an engaging and supportive learning environment.}
\resumeItemListEnd

\section{Projects}
\datedsubsection{\textbf{JobTrackPro}}{Dec 2024 – Present}
\resumeItemListStart
\resumeItem{Developing an AI-powered resume tailoring tool based on job descriptions using Claude API.}
\resumeItem{Built a job-tracking platform that scrapes LinkedIn/Indeed for data-driven application insights.}
\resumeItem{Designed an interface for managing job applications, statuses, deadlines, and reminders.}
\resumeItem{Tech stack: Django, Selenium, Pandas, MongoDB, Python, Vite, React, Firebase}
\resumeItemListEnd

\datedsubsection{\textbf{ShopEase}}{Feb 2024 – May 2024}
\resumeItemListStart
\resumeItem{Developed an e-commerce platform with a responsive React/Redux frontend.}
\resumeItem{Built RESTful APIs using Node.js/Express.js for products, auth, and order management.}
\resumeItem{Integrated MongoDB for scalable data storage and retrieval.}
\resumeItem{Tech stack: Redux, Express.js, MongoDB, Node.js, React}
\resumeItemListEnd

\datedsubsection{\textbf{Multi-Service App}}{Sept 2023 – Dec 2023}
\resumeItemListStart
\resumeItem{Developed a platform for users to list and request services like tutoring and carpooling.}
\resumeItem{Implemented user auth, real-time messaging, and location services with Google Maps.}
\resumeItem{Managed database modeling and REST API development with Spring Boot.}
\resumeItem{Tech stack: Spring Boot, REST APIs, WebSockets, MySQL, JUnit}
\resumeItemListEnd