\documentclass{resume}

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Eshanth Chinthareddy}
\address{Ames, Iowa \\ 612-461-6318 \\ chinthareddyeshanth@gmail.com}

\begin{document}

\begin{rSection}{Education}

{\bf Iowa State University} \hfill {Expected Graduation: Dec 2025}\\
Bachelor of Science in Software Engineering \\
GPA: 3.28

\end{rSection}


\begin{rSection}{Technical Skills}
\begin{itemize}
    \item Languages: C, C++, C\#, Python, Java, JavaScript, TypeScript, Assembly, HTML, CSS, Go, Rust
    \item Technologies: REST APIs, WebSockets, Postman, MySQL, MERN Stack, Matplotlib, Git, Docker, Kubernetes, GCP, AWS, Azure, Firebase, CI/CD, GraphQL, Terraform, NVIDIA Jetson, CStreamer
    \item Frameworks: [.NET](http://asp.net) Core, React, Angular, Spring Boot, Next.js, NestJS, Flask, FastAPI, Django, Express.js, Electron, TensorFlow, PyTorch
\end{itemize}
\end{rSection}

\begin{rSection}{Work Experience}

\textbf{Software Engineering Intern} \hfill May 2024 - Present\\
\textit{Thinix} \hfill Ames, IA
\begin{itemize}
    \itemsep -3pt {} \vspace{-2pt}
    \resumeItem{Developed interactive reporting tools to analyze system performance, improving decision-making.}
    \resumeItem{Optimized REST APIs with [ASP.NET](http://asp.net) Core and Entity Framework, reducing response times by 40\%.}
    \resumeItem{Integrated Dynatrace APM for monitoring, enhancing observability and response times.}
    \resumeItem{Improved performance with eager loading, lazy loading, and async processing, cutting load times by 30\%.}
\end{itemize}

\textbf{System Support Specialist} \hfill May 2023 - May 2024\\
\textit{Iowa State University} \hfill Ames, IA
\begin{itemize}
    \itemsep -3pt {} \vspace{-2pt}
    \resumeItem{Provided technical support and managed IT service tickets, troubleshooting issues.}
    \resumeItem{Utilized SCCM and JAMF for software deployment and configuration management.}
    \resumeItem{Streamlined hardware inventory tracking through automated processes.}
\end{itemize}

\textbf{Mathematics Grading Assistant} \hfill Jan 2023 - May 2023\\
\textit{Iowa State University} \hfill Ames, IA
\begin{itemize}
    \itemsep -3pt {} \vspace{-2pt}
    \resumeItem{Assessed quizzes and assignments, providing constructive feedback.}
    \resumeItem{Mentored students in calculus and algebra, conducting personalized tutoring sessions.}
    \resumeItem{Implemented effective teaching methodologies to foster an engaging learning environment.}
\end{itemize}

\end{rSection}

\begin{rSection}{Project Experience}

\textbf{Multi-Service App} \hfill Sept 2023 - Dec 2023\\
\textit{Spring Boot, REST APIs, WebSockets, MySQL, JUnit}
\begin{itemize}
    \itemsep -3pt {} \vspace{-2pt}
    \resumeItem{Developed a platform for users to list and request services like tutoring and carpooling.}
    \resumeItem{Implemented user authentication, real-time messaging, and location-based services.}
    \resumeItem{Managed database configurations and API development with Spring Boot.}
\end{itemize}

\textbf{ShopEase} \hfill Feb 2024 - May 2024\\
\textit{Redux, Express.js, MongoDB, Node.js, React}
\begin{itemize}
    \itemsep -3pt {} \vspace{-2pt}
    \resumeItem{Developed an e-commerce platform with seamless shopping experiences.}
    \resumeItem{Built responsive frontend using React and Redux for enhanced UX and state management.}
    \resumeItem{Designed REST APIs with Node.js and Express.js for product, user, and order management.}
    \resumeItem{Integrated MongoDB for scalable data storage and retrieval.}
\end{itemize}

\textbf{JobTrackPro} \hfill Dec 2024 - Present\\
\textit{Django, Selenium, Pandas, MongoDB, Python, Vite, React, Firebase, Claude API}
\begin{itemize}
    \itemsep -3pt {} \vspace{-2pt}
    \resumeItem{Developing an AI-powered resume tailoring tool based on job descriptions.}
    \resumeItem{Built a job-tracking platform that scrapes LinkedIn and Indeed for data-driven insights.}
    \resumeItem{Designed a UI for managing job applications, statuses, deadlines, and reminders.}
    \resumeItem{Implemented spreadsheet export for analyzing application trends.}
\end{itemize}

\end{rSection}

\end{document}