\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage{geometry}
\geometry{left=0.4in,top=0.4in,right=0.4in,bottom=0.4in}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\name}[1]{\centerline{\Huge \scshape #1}\vspace{1.25ex}}
\newcommand{\address}[1]{\centerline{#1}\vspace{-7pt}}
\newcommand{\basicInfo}[1]{\centerline{\small#1}\vspace{-7pt}}

\begin{document}
\name{Eshanth Chinthareddy}
\address{Ames, Iowa}
\phone{612-461-6318}
\email{chinthareddyeshanth@gmail.com}
\begin{resume}

\section{SUMMARY}
Software Engineering student actively seeking opportunities in embedded software development. Passionate about coding, problem-solving, and building scalable solutions. Proficient in C++, Python, and embedded development.

\section{EDUCATION}
\textbf{Iowa State University} \hfill Expected Graduation: Dec 2025 \\
Bachelor of Science in Software Engineering \hfill GPA: 3.28

\section{SKILLS}
\textbf{Languages:} C++, Python, C, C\#, Java, JavaScript, Assembly \\
\textbf{Embedded:} Microcontrollers, Microprocessors, NVIDIA Jetson, CStreamer \\
\textbf{Technologies:} .NET, REST APIs, Git, Docker, Kubernetes, CI/CD

\section{EXPERIENCE}
\textbf{Software Engineering Intern} \hfill May 2024 – Present \\
Thinix \hfill Ames, IA
\begin{itemize}
  \item Developed reporting tools with ASP.NET Core and Entity Framework, reducing response times by 40\%.
  \item Integrated Dynatrace APM for real-time monitoring, enhancing observability and performance.
  \item Led .NET 6 to .NET 8 migration, optimizing scalability and efficiency.
  \item Implemented automated testing pipelines with MSTest and Jest, increasing test coverage.
\end{itemize}

\textbf{System Support Specialist} \hfill May 2023 – May 2024 \\
Iowa State University \hfill Ames, IA
\begin{itemize}
  \item Provided frontline technical support, troubleshooting software/hardware issues.
  \item Utilized SCCM and JAMF for software deployment and device management.
  \item Managed IT service tickets, ensuring timely resolution of user requests.
\end{itemize}

\textbf{Mathematics Grading Assistant} \hfill Jan 2023 – May 2023 \\
Iowa State University \hfill Ames, IA  
\begin{itemize}
  \item Assessed quizzes and assignments, providing constructive feedback to students.
  \item Mentored students in calculus and algebra through personalized tutoring sessions.
  \item Implemented effective teaching methodologies to foster an engaging learning environment.
\end{itemize}

\section{PROJECTS}
\textbf{JobTrackPro} \hfill Dec 2024 – Present
\begin{itemize}
  \item Developing an AI-powered resume tailoring tool using Python, Django, and Claude API.
  \item Built a job-tracking platform that scrapes LinkedIn and Indeed for data-driven insights.
  \item Designed a user-friendly interface with React and Firebase for managing job applications.
\end{itemize}

\textbf{ShopEase} \hfill Feb 2024 – May 2024
\begin{itemize}
  \item Developed a full-stack e-commerce platform using React, Redux, Express.js, and MongoDB.
  \item Built RESTful APIs with Node.js and Express.js for product listings and order management.
  \item Integrated MongoDB for scalable database performance and dynamic data retrieval.
\end{itemize}

\textbf{Multi-Service App} \hfill Sept 2023 – Dec 2023
\begin{itemize} 
  \item Developed a multi-service platform with Spring Boot, REST APIs, and MySQL.
  \item Implemented user authentication, real-time messaging, and location-based services.
  \item Managed database configurations, data modeling, and API development.
\end{itemize}

\end{resume}
\end{document}